Contextuality and the Born rule in fuzzy quantum theories

### 2017-05-01 prop_letter.tex
prop_letter.tex Small things here and there...

Furthermore, if we express the observable~$\mathbf{O}$ as its spectrum
decomposition~$\sum_{i=1}^{N}\lambda_{i}P_{i}$, the expectation
value of $\mathbf{O}$ is given by~\cite{peres1995quantum,544199,Jaeger2007}
\begin{equation}
\expval{\mathbf{O}}_{\rho}=\Tr\left(\rho\mathbf{O}\right)=\sum_{i=1}^{N}\lambda_{i}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)\ .\label{eq:quantum-expectation}
\end{equation}

@@

Formally, we can ask: what can we deduce about the state of a quantum
system given a quantum interval-valued probability measure, i.e.,
given observations done with finite resources. Since the probabilities
are now intervals, it is intuitive to say a state~$\rho$ is consistent
with $\bar{\mu}$ on a projector~$P$ if $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
and denoted by $\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.
Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means $\rho$
is consistent with $\bar{\mu}$ on every projector in $S$.

@@

In the case that the intervals are infinitely precise, i.e., $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
any quantum probability measure can be recast as an interval-valued
one. For $d\ge3$, the question reduces to Gleason's theorem which
states that for any quantum IVPM~$\bar{\mu}$, there is an unique
state consistent with $\bar{\mu}$ on every projector.

While mapping to $\mathscr{I}_{\infty}$ is one extreme case of quantum
IVPM, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
is another one, and corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}.
However, before diving into the Kochen-Specker theorem, it is better
to understand how to define expectation value of an observable with
quantum IVPMs.

>>>>

Furthermore, if we express an observable~$\mathbf{O}$ as its spectrum
decomposition~$\sum_{i=1}^{N}\lambda_{i}P_{i}$, the expectation
value of $\mathbf{O}$ is given by~\cite{peres1995quantum,544199,Jaeger2007}
\begin{equation}
\expval{\mathbf{O}}_{\rho}=\Tr\left(\rho\mathbf{O}\right)=\sum_{i=1}^{N}\lambda_{i}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)\ .\label{eq:quantum-expectation}
\end{equation}

@@

Formally, we can ask: what can we deduce about the state of a quantum
system given a quantum IVPM, i.e., given observations done with finite
resources. Since the probabilities are now intervals, it is intuitive
to say a state~$\rho$ is consistent with $\bar{\mu}$ on a projector~$P$
if $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
and denoted by $\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.
Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means $\rho$
is consistent with $\bar{\mu}$ on every projector in $S$.

@@

In the case that the intervals are infinitely precise, i.e., $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
any quantum probability measure can be recast as an interval-valued
one. When $d\ge3$, the question reduces to Gleason's theorem which
states that for any quantum IVPM~$\bar{\mu}$, there is an unique
state consistent with $\bar{\mu}$ on every projector.

While mapping to $\mathscr{I}_{\infty}$ is one extreme case of quantum
IVPMs, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
is another one, corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}.
However, before diving into the Kochen-Specker theorem, it is better
to understand how to define the expectation value of an observable
with quantum IVPMs.
